---
title: "Multinomial Logistic Regression"
author: "祝尔康 2020012820"
date: "2022/12/20"
documentclass: ctexart
geometry: margin = 2cm
output:
  rticles::ctex: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(prompt = T, comment = '',collapse = T,message = F,warning = F,fig.align ='center', tidy = T)
```

```{r}
library(MASS)
library(dplyr)
library(tidyverse) 
library(caret)
library(nnet) # 另一个计算多项逻辑回归的库
library(car)
library(VGAM)
```

## 读取数据

```{r}
dat_std <- read.csv("std_bilibili.csv",header = T)[,6:17]
var_del_multiReg <- c("av_coin","av_danmu","num_fans") #去掉弹幕和投币数
dat_for_multiReg <- dplyr::select(dat_std,-var_del_multiReg)
dat_for_multiReg <- dat_for_multiReg[,c(1,3:9,2)]
dat_for_multiReg$fans_cat <-ifelse(test = dat_for_multiReg$fans_cat==0, yes = "small", 
                no = ifelse(test = dat_for_multiReg$fans_cat==1, yes = "middle", 
                  no = ifelse(test = dat_for_multiReg$fans_cat==2, yes = "big",no = "super big")))
dat_for_multiReg$fans_cat <- factor(dat_for_multiReg$fans_cat, levels = c("small","middle","big","super big"))
dat_for_multiReg$fans_cat <- relevel(dat_for_multiReg$fans_cat, ref = "small")
table(dat_for_multiReg$fans_cat)
head(dat_for_multiReg,3)
tail(dat_for_multiReg,3)
summary(dat_for_multiReg[,2:8])
```

响应变量：

(1)Multicategory *表示lasso下可丢变量

fans_cat: fans category，粉丝数的分类，0为很少，1为较少，2为较多，3为很多，记为小up主，中up主，大up主，超级up主，notated by[small,middle,big,super big] 

(2)continuous **表示lasso下可丢变量

num_fans: number of fans，粉丝数，单位为个

解释变量池：

(1)分类型变量

** gender: 性别，1为女性，0为男性

(2)连续型变量(将解释变量重新缩放到0和1之间，有时有助于参数估计的收敛。)

** num_videos: number of videos，视频数的多少，单位为个

num_charge: number of charges, 充电数的多少，单位为个

* av_coin: average number of 
coins，最近8个视频的平均投币量，单位为个

* av_danmu: average number of danmu, 最近8个视频的平均弹幕数量，单位为个

av_star: average number of stars, 最近8个视频的平均收藏量，单位为个

av_like: average number of likes, 最近8个视频的平均点赞数，单位为个

av_play: average number of plays, 最近8个视频的平均播放数，单位为次

av_comment: average number of comments, 最近8个视频的平均评论数，单位为个

av_share: average number of shares, 最近8个视频的平均分享数，单位为个

## 并行坐标图

```{r,echo=FALSE}
# 随机选取200个up主绘制并行坐标图
set.seed(123)
vis_sample <- dat_for_multiReg$fans_cat %>% 
  createDataPartition(p = 0.3, list = F)
blbl <- dat_for_multiReg[vis_sample,]
x11(width = 10, height = 6, pointsize = 8)
 
# Reorder variables because gender is binary (may distort plot)
# Create indicator variable for class
blbl2<-data.frame(kernel = 1:nrow(blbl), blbl[,2:8],  
       gender.new = ifelse(test = blbl$gender == 0, yes = 0, no = 1))

# Colors by condition:
blbl.colors<-ifelse(test = blbl$fans_cat=="small", yes = "black", 
                no = ifelse(test = blbl$fans_cat=="middle", yes = "red", 
                  no = ifelse(test = blbl$fans_cat=="big", yes = "blue",no = "green")))
# Line type by condition:
blbl.lty<-ifelse(test = blbl$fans_cat=="small", yes = "solid", 
            no = ifelse(test = blbl$fans_cat=="middle", yes = "longdash", 
              no = ifelse(test = blbl$fans_cat=="big", yes = "dotdash",no = "twodash")))
pdf(file = "d:\\RLearning\\HW_CDA\\project\\Figure_parcoord.pdf", width = 12, height = 6, colormodel = "cmyk")   
parcoord(x = blbl2, col = blbl.colors, lty = blbl.lty)  # Plot
legend(x = 5.55, y = 1.00, legend = c("small", "middle", "big","super big"), 
       lty = c("solid", "longdash", "dotdash","twodash"), col=c("black","red","blue","green"), cex=1.0, bty="n")
dev.off()  
```

![](Figure_parcoord.pdf){width=80%}


## Model 1: 采用Multinomial logistic regression model

```{r}
# 划分0.8为数据集，0.2为测试集
# set.seed(1220)
# training_sample <- dat_for_multiReg$fans_cat %>% 
#   createDataPartition(p = 0.8, list = F)
# dat_train <- dat_for_multiReg[training_sample,]
# dat_test <- dat_for_multiReg[-training_sample,]
```


```{r}
mod.fit <- multinom(formula = fans_cat~., data = dat_for_multiReg)
summary(mod.fit)
```

$$\pi_{small}=\frac{1}{1+\sum_{j=middle,\ big,\ super\ big}\exp\{\alpha_{j}+\beta_{j1}x_1+\cdots+\beta_{jp}x_p\}}$$
$$\pi_j=\frac{\exp(\alpha_j+\beta_{j1}x_1+\cdots+\beta_{jp}x_p)}{1+\sum_{j=middle,\ big,\ super\ big}\exp\{\alpha_{j}+\beta_{j1}x_1+\cdots+\beta_{jp}x_p\}},\ j=middle,big,super\ big$$

```{r}
Anova(mod.fit)
Anova(mod.fit.drop1)
```

```{r}
mod.fit.drop1 <- multinom(formula = fans_cat~gender+num_charge+av_star+av_like+av_play+av_comment+av_share, data = dat_for_multiReg)
summary(mod.fit.drop1)
```



```{r}
# pi.hat <- predict(object=mod.fit, newdata=dat_test, type="probs")
# predicted_fans_cat <- mod.fit %>% predict(dat_test)
# accuracy <- mean(predicted_fans_cat == dat_test$fans_cat); accuracy
```

### Plot num_charge only model 1 

```{r,echo=FALSE}
x11(width = 7, height = 6, pointsize = 12)

# Estimate model with density only
mod.fit.nom.charge<-multinom(formula = fans_cat ~ num_charge, data = dat_for_multiReg)
summary(mod.fit.nom.charge)
beta.hat<-coefficients(mod.fit.nom.charge)

# Create plotting area first to make sure get the whole region with respect to x-axis
pdf(file = "d:\\RLearning\\HW_CDA\\project\\Figure_charge_only.pdf", width = 7, height = 6, colormodel = "cmyk")   # Create plot for book
curve(expr = 1/(1 + exp(beta.hat[1,1] + beta.hat[1,2]*x) + exp(beta.hat[2,1] + beta.hat[2,2]*x)),
      ylab = expression(hat(pi)), xlab = "num_charge", ylim = c(0,1),
      xlim = c(0, 1), col = "black", lty = "solid", lwd = 2, n = 1000, type = "n",
      panel.first = grid(col = "gray", lty = "dotted"))
# Plot each pi_j
curve(expr = 1/(1 + exp(beta.hat[1,1] + beta.hat[1,2]*x) + exp(beta.hat[2,1] + beta.hat[2,2]*x) 
                + exp(beta.hat[3,1] + beta.hat[3,2]*x)),
  col = "black", lty = "solid", lwd = 2, n = 1000, add = TRUE,
  xlim = c(min(dat_for_multiReg$num_charge[dat_for_multiReg$fans_cat == "small"]),
           max(dat_for_multiReg$num_charge[dat_for_multiReg$fans_cat == "small"])),
  ylim = c(0,1))  # small

curve(expr = exp(beta.hat[1,1] + beta.hat[1,2]*x)/(1 + exp(beta.hat[1,1] + beta.hat[1,2]*x) 
                + exp(beta.hat[2,1] + beta.hat[2,2]*x) + exp(beta.hat[3,1] + beta.hat[3,2]*x)),
  col = "red", lty = "longdash", lwd = 2, n = 1000, add = TRUE,
  xlim = c(min(dat_for_multiReg$num_charge[dat_for_multiReg$fans_cat == "middle"]),
           max(dat_for_multiReg$num_charge[dat_for_multiReg$fans_cat == "middle"])),
  ylim = c(0,1))  # middle

curve(expr = exp(beta.hat[2,1] + beta.hat[2,2]*x)/(1 + exp(beta.hat[1,1] + beta.hat[1,2]*x) 
                + exp(beta.hat[2,1] + beta.hat[2,2]*x) + exp(beta.hat[3,1] + beta.hat[3,2]*x)),
  col = "blue", lty = "dotdash", lwd = 2, n = 1000, add = TRUE,
  xlim = c(min(dat_for_multiReg$num_charge[dat_for_multiReg$fans_cat == "big"]),
           max(dat_for_multiReg$num_charge[dat_for_multiReg$fans_cat == "big"])),
  ylim = c(0,1))  # big

curve(expr = exp(beta.hat[3,1] + beta.hat[3,2]*x)/(1 + exp(beta.hat[1,1] + beta.hat[1,2]*x) 
                + exp(beta.hat[2,1] + beta.hat[2,2]*x) + exp(beta.hat[3,1] + beta.hat[3,2]*x)),
  col = "green", lty = "twodash", lwd = 2, n = 1000, add = TRUE,
  xlim = c(min(dat_for_multiReg$num_charge[dat_for_multiReg$fans_cat == "super big"]),
           max(dat_for_multiReg$num_charge[dat_for_multiReg$fans_cat == "super big"])),
  ylim = c(0,1))  # super big

legend(x = 0.6, y = 0.8, legend=c("small", "middle", "big", "super big"), lty=c("solid","longdash","dotdash","twodash"),
  col=c("black","red","blue","green"), bty="n", lwd = c(2,2,2), seg.len = 4)
title("pihat for multinommial regression model")
dev.off()  # Create plot for book
```

```{r,echo=FALSE}
# Create plotting area first to make sure get the whole region with respect to x-axis
pdf(file = "d:\\RLearning\\HW_CDA\\project\\Figure_charge_only2.pdf", width = 7, height = 6, colormodel = "cmyk")  
curve(expr = 1/(1 + exp(beta.hat[1,1] + beta.hat[1,2]*x) + exp(beta.hat[2,1] + beta.hat[2,2]*x)),
      ylab = expression(hat(pi)), xlab = "num_charge", ylim = c(0,1),
      xlim = c(0, 1), col = "black", lty = "solid", lwd = 2, n = 1000, type = "n",
      panel.first = grid(col = "gray", lty = "dotted"))
# Plot each pi_j
curve(expr = 1/(1 + exp(beta.hat[1,1] + beta.hat[1,2]*x) + exp(beta.hat[2,1] + beta.hat[2,2]*x) 
                + exp(beta.hat[3,1] + beta.hat[3,2]*x)),
  col = "black", lty = "solid", lwd = 2, n = 1000, add = TRUE,  ylim = c(0,1))  # small

curve(expr = exp(beta.hat[1,1] + beta.hat[1,2]*x)/(1 + exp(beta.hat[1,1] + beta.hat[1,2]*x) 
                + exp(beta.hat[2,1] + beta.hat[2,2]*x) + exp(beta.hat[3,1] + beta.hat[3,2]*x)),
  col = "red", lty = "longdash", lwd = 2, n = 1000, add = TRUE, ylim = c(0,1))  # middle

curve(expr = exp(beta.hat[2,1] + beta.hat[2,2]*x)/(1 + exp(beta.hat[1,1] + beta.hat[1,2]*x) 
                + exp(beta.hat[2,1] + beta.hat[2,2]*x) + exp(beta.hat[3,1] + beta.hat[3,2]*x)),
  col = "blue", lty = "dotdash", lwd = 2, n = 1000, add = TRUE, ylim = c(0,1))  # big

curve(expr = exp(beta.hat[3,1] + beta.hat[3,2]*x)/(1 + exp(beta.hat[1,1] + beta.hat[1,2]*x) 
                + exp(beta.hat[2,1] + beta.hat[2,2]*x) + exp(beta.hat[3,1] + beta.hat[3,2]*x)),
  col = "green", lty = "twodash", lwd = 2, n = 1000, add = TRUE,ylim = c(0,1)) # super big

legend(x = 0.6, y = 0.8, legend=c("small", "middle", "big", "super big"), lty=c("solid","longdash","dotdash","twodash"),
  col=c("black","red","blue","green"), bty="n", lwd = c(2,2,2), seg.len = 4)
title("pihat for multinommial regression model")
dev.off()  # Create plot for book
```

![](Figure_charge_only.pdf){width=50%}
![](Figure_charge_only2.pdf){width=50%}




## Model 2: 采用ordinal response regression models

假定：small($Y=1$)<middle($Y=2$)<big($Y=3$)<super big($Y=4$)

```{r}
levels(dat_for_multiReg$fans_cat)
mod.fit.ord <- MASS::polr(formula = fans_cat~., data = dat_for_multiReg, method = "logistic")
summary(mod.fit.ord)
Anova(mod.fit.ord)
```

```{r}
drop1(mod.fit.ord)
# 删除av_comment
mod.fit.ord.drop1 <- MASS::polr(formula = fans_cat~gender+num_videos+num_charge+av_star+av_like+av_play+av_share, data = dat_for_multiReg, method = "logistic")
drop1(mod.fit.ord.drop1)
# 删除num_videos
mod.fit.ord.drop2 <- MASS::polr(formula = fans_cat~gender+num_charge+av_star+av_like+av_play+av_share, data = dat_for_multiReg, method = "logistic")
drop1(mod.fit.ord.drop2)
# 删除gender
mod.fit.ord.drop3 <- MASS::polr(formula = fans_cat~num_charge+av_star+av_like+av_play+av_share, data = dat_for_multiReg, method = "logistic")
drop1(mod.fit.ord.drop3)
Anova(mod.fit.ord.drop3)
```

polr() function estimates the model:
$$\operatorname{logit}(P(Y \leq j))=\alpha_{j}-\eta_1 x_1-\cdots-\eta_p x_p$$
The estimated model:
$$\operatorname{logit}(\hat P(Y \leq j))=\hat\alpha_{j}+0.35gender -0.46num\_vedios-24num\_charge+4.9av\_star-23av\_like-18av\_play+5.1av\_comment+3.2av\_share$$
$$\hat\alpha_{1}=-0.32,\ \hat\alpha_{1}=0.98,\ \hat\alpha_{3}=-2.47$$

```{r}
# pi.hat.ord <- predict(object = mod.fit.ord3, type = "probs")
# predicted_fans_cat_ord <- mod.fit.ord3 %>% predict(dat_test)
# accuracy.ord <- mean(predicted_fans_cat_ord == dat_test$fans_cat); accuracy.ord
```

### Plot num_charge only model 2

```{r}
mod.fit.ord.charge<-polr(formula=fans_cat~num_charge, data = dat_for_multiReg, method = "logistic")
summary(mod.fit.ord.charge)
```

```{r,echo=FALSE}
x11(width = 7, height = 6, pointsize = 12)

# Create plotting area first to make sure get the whole region with respect to x-axis
lwd.po = 2
pdf(file = "d:\\RLearning\\HW_CDA\\project\\Figure_propotional.pdf", width = 7, height = 6, colormodel = "cmyk")
curve(expr = plogis(q = mod.fit.ord.charge$zeta[1] - mod.fit.ord.charge$coefficients*x),
      ylab = expression(hat(pi)), xlab = "num_charge", ylim = c(0,1),
      xlim = c(0, 1), col = "black", lty = "solid", lwd = lwd.po, n = 1000, type = "n",
      panel.first = grid(col = "gray", lty = "dotted"))

# Plot each pi_j for proportional odds mode
curve(expr = plogis(q = mod.fit.ord.charge$zeta[1] - mod.fit.ord.charge$coefficients*x),
  type = "l", col = "black", lty = "solid", lwd = lwd.po, n = 1000, add = TRUE,
  xlim = c(min(dat_for_multiReg$num_charge[dat_for_multiReg$fans_cat == "small"]),
           max(dat_for_multiReg$num_charge[dat_for_multiReg$fans_cat == "small"])),
  ylim = c(0,1))  # small

curve(expr = plogis(q = mod.fit.ord.charge$zeta[2] - mod.fit.ord.charge$coefficients*x) - 
        plogis(q = mod.fit.ord.charge$zeta[1] - mod.fit.ord.charge$coefficients*x),
  type = "l", col = "red", lty = "longdash", lwd = lwd.po, n = 1000, add = TRUE,
  xlim = c(min(dat_for_multiReg$num_charge[dat_for_multiReg$fans_cat == "middle"]),
           max(dat_for_multiReg$num_charge[dat_for_multiReg$fans_cat == "middle"])),
  ylim = c(0,1))  # middle

curve(expr = plogis(q = mod.fit.ord.charge$zeta[3] - mod.fit.ord.charge$coefficients*x) - 
        plogis(q = mod.fit.ord.charge$zeta[2] - mod.fit.ord.charge$coefficients*x),
  type = "l", col = "blue", lty = "dotdash", lwd = lwd.po, n = 1000, add = TRUE,
  xlim = c(min(dat_for_multiReg$num_charge[dat_for_multiReg$fans_cat == "big"]),
           max(dat_for_multiReg$num_charge[dat_for_multiReg$fans_cat == "big"])),
  ylim = c(0,1))  # big

curve(expr = 1 - plogis(q = mod.fit.ord.charge$zeta[3] - mod.fit.ord.charge$coefficients*x),
  type = "l", col = "green", lty = "twodash", lwd = lwd.po, n = 1000, add = TRUE,
  xlim = c(min(dat_for_multiReg$num_charge[dat_for_multiReg$fans_cat == "super big"]),
           max(dat_for_multiReg$num_charge[dat_for_multiReg$fans_cat == "super big"])),
  ylim = c(0,1))  # super big

legend(x = 0.6, y = 0.8, legend=c("small", "middle", "big", "super big"), lty=c("solid","longdash","dotdash","twodash"), col=c("black","red","blue","green"),
       bty="n", lwd = c(2,2,2,2), seg.len = 4)
title("pihat for proportional odds model")
dev.off() 
```

```{r,echo=FALSE}
x11(width = 7, height = 6, pointsize = 12)

# Create plotting area first to make sure get the whole region with respect to x-axis
lwd.po = 2
pdf(file = "d:\\RLearning\\HW_CDA\\project\\Figure_propotional2.pdf", width = 7, height = 6, colormodel = "cmyk")
curve(expr = plogis(q = mod.fit.ord.charge$zeta[1] - mod.fit.ord.charge$coefficients*x),
      ylab = expression(hat(pi)), xlab = "num_charge", ylim = c(0,1),
      xlim = c(0, 1), col = "black", lty = "solid", lwd = lwd.po, n = 1000, type = "n",
      panel.first = grid(col = "gray", lty = "dotted"))

# Plot each pi_j for proportional odds model
curve(expr = plogis(q = mod.fit.ord.charge$zeta[1] - mod.fit.ord.charge$coefficients*x),
  type = "l", col = "black", lty = "solid", lwd = lwd.po, n = 1000, add = TRUE,
  ylim = c(0,1))  # small

curve(expr = plogis(q = mod.fit.ord.charge$zeta[2] - mod.fit.ord.charge$coefficients*x) - 
        plogis(q = mod.fit.ord.charge$zeta[1] - mod.fit.ord.charge$coefficients*x),
  type = "l", col = "red", lty = "longdash", lwd = lwd.po, n = 1000, add = TRUE,
  ylim = c(0,1))  # middle

curve(expr = plogis(q = mod.fit.ord.charge$zeta[3] - mod.fit.ord.charge$coefficients*x) - 
        plogis(q = mod.fit.ord.charge$zeta[2] - mod.fit.ord.charge$coefficients*x),
  type = "l", col = "blue", lty = "dotdash", lwd = lwd.po, n = 1000, add = TRUE,
  ylim = c(0,1))  # big

curve(expr = 1 - plogis(q = mod.fit.ord.charge$zeta[3] - mod.fit.ord.charge$coefficients*x),
  type = "l", col = "green", lty = "twodash", lwd = lwd.po, n = 1000, add = TRUE,
  ylim = c(0,1))  # super big

legend(x = 0.6, y = 0.8, legend=c("small", "middle", "big", "super big"), lty=c("solid","longdash","dotdash","twodash"), col=c("black","red","blue","green"), 
       bty="n", lwd = c(2,2,2,2), seg.len = 4)
title("pihat for proportional odds model")
dev.off() 
```

![](Figure_propotional.pdf){width=50%}
![](Figure_propotional2.pdf){width=50%}

### 绘制累积概率分布图

```{r,echo=FALSE}
x11(width = 7, height = 6, pointsize = 12)

# Create plotting area first to make sure get the whole region with respect to x-axis
lwd.po = 2
pdf(file = "d:\\RLearning\\HW_CDA\\project\\Figure_cumulative.pdf", width = 7, height = 6, colormodel = "cmyk")
curve(expr = plogis(q = mod.fit.ord.charge$zeta[1] - mod.fit.ord.charge$coefficients*x),
      ylab = expression(hat(pi)), xlab = "num_charge", ylim = c(0,1),
      xlim = c(0, 1), col = "black", lty = "solid", lwd = lwd.po, n = 1000, type = "n",
      panel.first = grid(col = "gray", lty = "dotted"))

# Plot each pi_j for proportional odds model
# Plot each pi_j
curve(expr = plogis(q = mod.fit.ord.charge$zeta[1] - mod.fit.ord.charge$coefficients*x),
  type = "l", col = "black", lty = "solid", lwd = lwd.po, n = 1000, add = TRUE,
  xlim = c(0, 1), ylim = c(0,1))  # small

curve(expr = plogis(q = mod.fit.ord.charge$zeta[2] - mod.fit.ord.charge$coefficients*x),
  type = "l", col = "red", lty = "longdash", lwd = lwd.po, n = 1000, add = TRUE,
  xlim = c(0, 1), ylim = c(0,1))  # small or middle

curve(expr = plogis(q = mod.fit.ord.charge$zeta[3] - mod.fit.ord.charge$coefficients*x), 
  type = "l", col = "blue", lty = "dotdash", lwd = lwd.po, n = 1000, add = TRUE,
  xlim = c(0, 1), ylim = c(0,1))  # small or middle or big

legend(x = 0.5, y = 0.8, legend=c("Y less than or equal to 1", "Y less than or equal to 2", 
                                  "Y less than or equal to 3"), lty=c("solid","longdash","dotdash"),
  col=c("black","red","blue"), bty="n", lwd = c(2,2,2), seg.len = 4)
title("cumulative pihat")
dev.off() 
```

![](Figure_cumulative.pdf){width=80%}



## Model 3: 采用Non-proportional odds model

```{r}
mod.fit.po <- vglm(formula = fans_cat~., data = dat_for_multiReg, family = cumulative(parallel = T))
summary(mod.fit.po)
```

```{r}
mod.fit.npo <- vglm(formula = fans_cat~., family = cumulative(parallel = F), data = dat_for_multiReg)
summary(mod.fit.npo)
```

```{r}
Anova(mod.fit.po)

Anova(mod.fit.npo)
```

```{r}
# x <- mod.fit.npo %>% predict(dat_test,type = 'response')
# predicted_fans_cat_npo <- apply(x, 1, function(t) colnames(x)[which.max(t)])
# accuracy.npo <- mean(predicted_fans_cat_npo == dat_test$fans_cat); accuracy.npo
```


## 模型比较

### 比较非平行和平行模型

```{r}
dev.po <- deviance(mod.fit.po)
dev.npo <- deviance(mod.fit.npo)
LR.stat <-  dev.po - dev.npo
df <- df.residual(mod.fit.po)-df.residual(mod.fit.npo)
p.value <- 1 - pchisq(q = LR.stat, df = df)

data.frame(dev.po,dev.npo,LR.stat, df, p.value)
```

```{r}
mod.fit.npo.charge <- vglm(formula = fans_cat~num_charge, family = cumulative(parallel = F), data = dat_for_multiReg)
summary(mod.fit.npo.charge)
cf <- coef(mod.fit.npo.charge) 
```


```{r}
x11(width = 7, height = 6, pointsize = 12)

# Create plotting area first to make sure get the whole region with respect to x-axis
lwd.po = 2
pdf(file = "d:\\RLearning\\HW_CDA\\project\\Figure_npo_charge.pdf", width = 7, height = 6, colormodel = "cmyk")
curve(expr = plogis(q = cf[1] + cf[4]*x),
      ylab = expression(hat(pi)), xlab = "num_charge", ylim = c(0,1),
      xlim = c(0, 1), col = "black", lty = "solid", lwd = lwd.po, n = 1000, type = "n",
      panel.first = grid(col = "gray", lty = "dotted"))

# Plot each pi_j for proportional odds mode
curve(expr = plogis(q = cf[1] + cf[4]*x),
  type = "l", col = "black", lty = "solid", lwd = lwd.po, n = 1000, add = TRUE,
  xlim = c(min(dat_for_multiReg$num_charge[dat_for_multiReg$fans_cat == "small"]),
           max(dat_for_multiReg$num_charge[dat_for_multiReg$fans_cat == "small"])),
  ylim = c(0,1))  # small

curve(expr = plogis(q =cf[2] + cf[5]*x) - plogis(q = cf[1] + cf[4]*x),
  type = "l", col = "red", lty = "longdash", lwd = lwd.po, n = 1000, add = TRUE,
  xlim = c(min(dat_for_multiReg$num_charge[dat_for_multiReg$fans_cat == "middle"]),
           max(dat_for_multiReg$num_charge[dat_for_multiReg$fans_cat == "middle"])),
  ylim = c(0,1))  # middle

curve(expr =  plogis(q =cf[3] + cf[6]*x) - plogis(q = cf[2] + cf[5]*x),
  type = "l", col = "blue", lty = "dotdash", lwd = lwd.po, n = 1000, add = TRUE,
  xlim = c(min(dat_for_multiReg$num_charge[dat_for_multiReg$fans_cat == "big"]),
           max(dat_for_multiReg$num_charge[dat_for_multiReg$fans_cat == "big"])),
  ylim = c(0,1))  # big

curve(expr = 1 - plogis(q =cf[3] + cf[6]*x),
  type = "l", col = "green", lty = "twodash", lwd = lwd.po, n = 1000, add = TRUE,
  xlim = c(min(dat_for_multiReg$num_charge[dat_for_multiReg$fans_cat == "super big"]),
           max(dat_for_multiReg$num_charge[dat_for_multiReg$fans_cat == "super big"])),
  ylim = c(0,1))  # super big

legend(x = 0.6, y = 0.8, legend=c("small", "middle", "big", "super big"), lty=c("solid","longdash","dotdash","twodash"), col=c("black","red","blue","green"),
       bty="n", lwd = c(2,2,2,2), seg.len = 4)
title("pihat for proportional odds model")
dev.off() 
```






